Manuscript simulations

### 2023-03-03 Manuscript simulations.Rmd
toying with sum-to-zero constraints
finished simulation functions, time to let them run!

```{r}

```

@@

```{r}
rm(list = ls())
source("simulations_helpers.R")
source("coral.R")
```

@@

```{r}
test <- one_sim(
  mat = compas_data[[1]][[1]]$Y,
  true_coords = compas_data[[1]][[1]]$true_coords,
  k = 2, 
  sim = 1, 
  niter = 100000,
  nchains = 3,
  nburnin = 50000,
  thin = 5,
  max_clus = 8,
  max_attempts = 10
)
```

>>>>

@@

```{r}
rm(list = ls())
source("simulations_helpers.R")
# source("coral.R")
```

@@

```{r, eval = F}
test <- one_sim(
  mat = compas_data[[1]][[1]]$Y,
  true_coords = compas_data[[1]][[1]]$true_coords,
  k = 2, 
  sim = 1, 
  niter = 150000,
  nchains = 3,
  nburnin = 100000,
  thin = 5,
  max_clus = 8,
  max_attempts = 6
)
```

```{r}
# run sims
sim_tbl <- tibble(
  k = rep(2:5, each = 100),
  sim = rep(1:100, length(2:5))
)
run_sims <- function(sim_tbl, niter = 150000, nchains = 3, nburnin = 100000, thin = 5, max_clus = 8, max_attempts = 6){
  out <- list()
  for(i in 1:nrow(sim_tbl)){
    # message
    message(paste0("Beginning sim ", i, " of ", nrow_sim_tbl))

    # grab sim params
    k_ <- sim_tbl$k[i]
    sim_ <- sim_tbl$sim[i]

    # run one sim
    onerun <- one_sim(
      mat = compas_data[[k_]][[sim_]]$Y,
      true_coords = compas_data[[k_]][[sim_]]$true_coords,
      k = k_, 
      sim = sim_, 
      niter = niter,
      nchains = nchains,
      nburnin = nburnin,
      thin = thin,
      max_clus = max_clus,
      max_attempts = max_attempts
    )
    saveRDS(
      onerun, 
      paste0("simulations/agg_summaries/", onerun, "_", i, ".rds")
    )
    out[[i]] <- onerun
  }
  return(out)
}
sims <- run_sims(
  sim_tbl,
  niter = 150000, 
  nchains = 3,
  nburnin = 100000, 
  thin = 5, 
  max_clus = 8, 
  max_attempts = 6
)
saveRDS(sims, "simulations/agg_summaries/sims.rds")
```
